---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dryingfaecal

<!-- badges: start -->
<!-- badges: end -->

## Introduction 
The data is related to the drying process of faecal sludge and was collected from different institutions with relevant information about the feedstock and experimental conditions. 
Experimental data is categorized into 8 groups: thermodynamics, kinetics, physiochemical properties, morphology, mechanical properties, dewaterability, disinfection, and gas emission. 

Different types of faecal samples were involved on the generation of the data: 
- fresh faeces and faecal sludge from various types of onsite sanitation facilities, among which ventilated improved pit (VIP) latrines
- urine diversion dry toilets (UDDT)
- anaerobic baffled reactor (ABR) from a decentralized wastewater treatment plant (DEWAT)
TODO: INSERT PICTURES?
## Installation

You can install the development version of dryingfaecal from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/dryingfaecal")
```


## Example

``` {r} 
library(dryingfaecal)

## basic example code
addendum |> 
  head() |>
  tibble::as_tibble()
```
The dataset contains the following variables:
```{r, echo=FALSE}
readr::read_csv("data-raw/dictionary.csv", show_col_types = FALSE) |>
  knitr::kable()
```

## Categories
### Dewatering
Experiment: Centrifugation done in a centrifuge HERMLE Z323, during 120 minutes at a rate of 5000 RPM, for 40 g of sample per centrifuge tube

